The Unicode Cookbook \linebreak for Linguists

### 2015-10-17 book/unicode.tex
some general knitr settings added

\documentclass[output=inprep,
%  long|short|inprep
%  ,blackandwhite
%  ,smallfont
%  ,draftmode  
		biblatex
		]{LSP/langsci}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                                              %%%
%%%             Frontmatter                      %%%
%%%                                              %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\frontmatter
% %% uncomment if you have preface and/or acknowledgements
% \include{chapters/preface}
% \include{chapters/acknowledgments}
% \include{chapters/abbreviations}
\tableofcontents
\mainmatter%

@@

>>>>

\documentclass[output=inprep,
%  long|short|inprep
%  ,blackandwhite
%  ,smallfont
%  ,draftmode  
		biblatex
		]{LSP/langsci}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0, 0, 0}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.533,0,0.133}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.667,0.267,0}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{1,0.533,0}{#1}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.4,0.067,0.067}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0,0,0.4}{\textbf{#1}}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0,0,0.4}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0,0.267,0.4}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                                              %%%
%%%             Frontmatter                      %%%
%%%                                              %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
\frontmatter
% %% uncomment if you have preface and/or acknowledgements
% \include{chapters/preface}
% \include{chapters/acknowledgments}
% \include{chapters/abbreviations}
\tableofcontents
\mainmatter%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                                              %%%
%%%             knitr settings                   %%%
%%%                                              %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% for themes, see:
% https://rclickhandbuch.files.wordpress.com/2014/09/knitrthemesoverview.pdf

@@

\chapter{Testing code inclusing}

Trying to include code through knitr. Different languages can be easily 
included!

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.965, 0.965, 0.965}\color{fgcolor}\begin{kframe}
\begin{alltt}
echo 'this is a simple bash example'
ls | wc
\end{alltt}

\begin{verbatim}
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.965, 0.965, 0.965}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstr{'R works out of the box'}
\end{alltt}
\begin{verbatim}
## [1] "R works out of the box"
\end{verbatim}
\begin{alltt}
\hlstd{(x} \hlkwb{<-} \hlnum{3}\hlopt{+}\hlnum{4}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] 7
\end{verbatim}
\begin{alltt}
\hlkwd{Sys.getlocale}\hlstd{(}\hlstr{"LC_CTYPE"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] "en_US.UTF-8"
\end{verbatim}
\begin{alltt}
\hlstr{'aɽɮz'}
\end{alltt}
\begin{verbatim}
## [1] "aɽɮz"
\end{verbatim}
\end{kframe}
\end{knitrout}

You can refer to variables by using \textbackslash Sexpr{}. 
I think 7 is an interesting number!

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.965, 0.965, 0.965}\color{fgcolor}\begin{kframe}
\begin{alltt}
'python also works!'
print('bla' + 'bla')
print(3+4)
\end{alltt}

\begin{verbatim}
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

You have to add the option `engine.paht='python3'' to get Python r

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.965, 0.965, 0.965}\color{fgcolor}\begin{kframe}
\begin{alltt}
print('python3 needs an extra tag')
uni = 'aɽɮz'
print(uni)
\end{alltt}

\begin{verbatim}
## python3 needs an extra tag
## aɽɮz
\end{verbatim}
\end{kframe}
\end{knitrout}

Testing: does referencing to variables also work in Python? It does give an error, so no... !
